GBIF invasive species

### 2021-04-09 analysis/invasive_data.Rmd
Function to read in invasive species data

```{r}
library(tidyverse)
library(rgbif)
library(geonames)
```

@@

get_country <- function(study_id, cent_lat, cent_long){
  con_data <- get_GNcountry(lat = cent_lat, lng = cent_long, lang = "en", radius = 50)
  name <- ifelse(length(con_data) == 1, con_data, con_data$countryName)

@@

country_data <- pmap_dfr(meta, get_country) %>%
  #hand resolve study_ids in the ocean
  mutate(country = case_when(
  study_id == 108 ~ "Namibia", 
  study_id %in% c(166, 169) ~ "United States", 
  study_id == 172 ~ "Morocco", 
  TRUE ~ country
))

@@

taxon <- read_tsv(paste0(invasive_files[2], "/", "taxon.txt"))
profile <- read_tsv(paste0(invasive_files[2], "/", "speciesprofile.txt"))
dist <- read_tsv(paste0(invasive_files[2], "/", "distribution.txt")) %>%
  select(id, countryCode)

data <- left_join(taxon, profile) %>% left_join(dist)

>>>>

```{r}
library(tidyverse)
library(rgbif)
library(geonames)
library(countrycode)
library(taxadb)
```

@@

get_country <- function(study_id, cent_lat, cent_long){
  #con_data <- get_GNcountry(lat = cent_lat, lng = cent_long, lang = "en", radius = 50)
  con_data <- get_GNcountry(lat = cent_lat, lng = cent_long, radius = 50)
  name <- ifelse(length(con_data) == 1, con_data, con_data$countryName)

@@

country_data <- pmap_dfr(meta, get_country) %>%
  #hand resolve study_ids in the ocean
  mutate(country = case_when(
  study_id == 108 ~ "Namibia", 
  study_id %in% c(56, 166, 169) ~ "United States", 
  study_id == 172 ~ "Morocco", 
  TRUE ~ country
)) %>%
  mutate(code = countryname(country, destination = "genc2c")) %>%
  mutate(code = case_when(
    code == "CA" ~ "US", 
    code == "PR" ~ "DO",
    TRUE ~ code
  ))

@@

invasive_data <- map_dfr(invasive_files[2:21], function(x){
  taxon <- read_tsv(paste0(x, "/", "taxon.txt"))
  profile <- read_tsv(paste0(x, "/", "speciesprofile.txt"))
  dist <- read_tsv(paste0(x, "/", "distribution.txt")) %>%
    select(id, countryCode)

  data <- left_join(taxon, profile) %>% left_join(dist)
  return(data)
})
```

Substituting years:
- orig: Canada, data: United States
- orig: Puerto Rico, data: Dominican Republic
